Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-11-14 paper/paper1/ms.tex
Orbital parameters based on TESS data
Checkout out some archival datasets--- mostly red herrings
Add a paragraph about Dasch non-constraints

Here we present a study of the exosphere of HAT-P-67b.  HAT-P-67 is a binary system of an F type sub-giant and a much cooler M2 star with the Saturn-sized planet HAT-P-67b.  HAT-P-67b stands out for a few reasons.  It has a relatively low surface gravity, which could make it amenable to rapid atmospheric mass loss, all else being equal.  It orbits an evolved star, which means it could have changed its instellation recently as the star's size and radiaiton properties have changed.  The star appears close to the star, making it conceivable that star-planet interactions could be at play.  These and other reasons make HAT-P-67b a unique laboratory for measuring the properties of exospheres and their interactions with their host stars.

@@

@@

@@

\begin{deluxetable*}{lrrrh}
    \tablewidth{0pc}
    \tabletypesize{\scriptsize}
    \tablecaption{
        Revised orbital and planetary parameters
        \label{tabOrbit}
    }
    \tablehead{
        \colhead{Parameter}   &
        \colhead{Zhou et al. 2017} &
        \colhead{Ivshina \& Winn 2022} &
        \colhead{This Work} &
        \nocolhead{Alternate}
    }
    \startdata
    %%
    ~~~$P$ (days)             \dotfill    & $4.8101025_{-0.00000033}^{+0.00000043}$ & x & y & z \\
    ~~~$T_c$ (${\rm BJD}$)  \dotfill    & $2455961.38467_{-0.00064}^{+0.00076}$ & x & y & z \\
    ~~~$T_{14}$ (days)  \dotfill    & $0.2912 \pm 0.0019$ & x & y & z \\
    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ & x & y & z \\
    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ & x & y & z \\
    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ & x & y & z \\
    ~~~$b \equiv a \cos i/\rstar$
    \dotfill    & $0.12_{-0.08}^{+0.12}$ & x & y & z \\
    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ & x & y & z \\
    \enddata
\end{deluxetable*}

>>>>

Here we present a study of the exosphere of HAT-P-67b.  HAT-P-67 is an F type sub-giant with the Saturn-sized planet HAT-P-67b.  HAT-P-67b stands out for a few reasons.  It has a relatively low surface gravity, which could make it amenable to rapid atmospheric mass loss.  It orbits an evolved star, which means its instellation may have increased as the star's size has grown.  The star appears close to the star, making it conceivable that star-planet interactions could be at play.  These and other reasons make HAT-P-67b a unique laboratory for measuring the properties of exospheres and their interactions with their host stars.  The system appears to consist of a binary with an M dwarf companion HAT-P-67B separated by $9\farcs0$.

@@

\subsection{DASCH}
We searched for observations of HAT-P-67 in other archives.  It appears in the Harvard Plate Archive, with 5809 measurements digitized through DASCH \censorbox{citation}, spanning over 120 years of coarse photometric monitoring.  In principle these datasets could inform long-term variability trends such as stellar cycles.  In practice the 0.15 magnitude jitter appears too coarse to perceive any genuine astrophysical variability, with no conspicuous trend seen.  We can therefore place a relatively mild constraint that the star is stable at the $30\%$ level over periods of tens of years.

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../../figures/Gaia_HAT_P_67_AB.png}
    \caption{HR Diagram of F star HAT-P-67A with its assumed M-dwarf main sequence companion HAT-P-67B.  The density of stars comes from the \emph{Kepler} prime field estimated by \citet{2020AJ....160..108B} using \emph{Gaia DR2}.}
    \label{fig:gaiaHRD}
\end{figure}

@@

\begin{deluxetable*}{lrrrh}
    \tablewidth{0pc}
    \tabletypesize{\scriptsize}
    \tablecaption{
        Revised orbital and planetary parameters
        \label{tabOrbit}
    }
    \tablehead{
        \colhead{Parameter}   &
        \colhead{Zhou et al. 2017} &
        \colhead{Ivshina \& Winn 2022} &
        \colhead{This Work} &
        \nocolhead{Alternate}
    }
    \startdata
    %%
    ~~~$P$ (days)             \dotfill    & $4.8101025_{-3.3\times 10^{-7}}^{+4.3\times 10^{-7}}$ & 4.8101046$\pm1.7\times10^{-6}$ & 4.81011 & z \\
    ~~~$T_c$ (${\rm BTJD}$)  \dotfill    & $-1038.61533_{-0.00064}^{+0.00076}$ & 1958.08059$\pm$0.00032 & 1958.07933 & z \\
    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ & x & 7.0636 & z \\
    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ & x & y & z \\
    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ & x & y & z \\
    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ & x & 0.08231 & z \\
    ~~~$b \equiv a \cos i/\rstar$
    \dotfill    & $0.12_{-0.08}^{+0.12}$ & x & 0.45616 & z \\
    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ & x & y & z \\
    \enddata
\end{deluxetable*}
